Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-11-21 ms/main.tex
todo
Add panel D

\begin{figure}[p]
  \centering       
    \includegraphics[width=0.45\textwidth]{Result2_c_zero_alpha.eps}
	~
    \includegraphics[width=0.45\textwidth]{Result2_c_non_zero_alpha.eps}
    ~
    \includegraphics[width=0.45\textwidth]{Result2_alpha.eps}    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission (v=1).} 
The figure shows the parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
(\textbf{a-b})~Cost of cooperation $c$ is on the y-axis; the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively. 
(\textbf{c})~Social association $\alpha$ is on the y-axis; the social association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
Here, $b=1.3$, $T_A=0.4$, (\textbf{a})~$\alpha = 0$,(\textbf{b})~$\alpha = 0.7$, (\textbf{c})~$c = 0.35$.
  	}
    \label{fig:equilibria_v1}
\end{figure}
%TODO add panel d?
% maybe show cost vs alpha ?

@@

%%% Figure: polymorphism map
\begin{figure}[p]
  \centering
    \includegraphics[scale=0.4]{coexistence_without_oblique.eps}
    \includegraphics[scale=0.4]{coexistence_with_oblique.eps}
  \caption{\textbf{Stable and unstable polymorphism of cooperation and defection.}
  The curves show the change in cooperators frequency, $\hat{p}'-\hat{p}$, as a function of the current frequency of cooperators among juveniles, $\hat{p}$ (\autoref{eq:nextgen_juveniles}).
  The dashed black line is $\hat{p}'-\hat{p}=0$.
  The curves and the dashed line intersect at the polymorphic equilibrium $\hat{p}^*$ (red circle).
  %When $\hat{p}' - \hat{p} > 0 $,  $\hat{p}$ increases towards $\hat{p}^*$.
  %When $\hat{p}' - \hat{p} < 0$, $\hat{p}$ decreases towards $\hat{p}^*$.
  \textbf{(a)} Without oblique transmission, $v=1$.
  A stable polymorphism (orange curve) is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$.
  An unstable polymorphism (blue curve) is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$.
  \textbf{(b)} With oblique transmission. 
  A stable polymorphism (orange curve) is given by $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$.
  An unstable polymorphism (blue curve) is given by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $\alpha = 0.09$ and $v=0.6$.
  }
  \label{fig:polymorphism_recursive}
  \end{figure}

>>>>

\begin{figure}[p]
  \centering       
    \includegraphics[width=0.45\textwidth]{Result2_c_zero_alpha.eps}
	  ~
    \includegraphics[width=0.45\textwidth]{Result2_c_non_zero_alpha.eps}
    ~
    \includegraphics[width=0.45\textwidth]{Result2_alpha.eps}   
    ~
    \includegraphics[width=0.45\textwidth]{coexistence_without_oblique.eps}
    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission (v=1).} 
    Figures \textbf{(a)-(c)} shows the parameter ranges for global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable polymorphism (blue), and stable polymorphism of cooperation and defection (yellow).
    In figures \textbf{(a)-(c)} the horizontal bias ($T_A-T_B$) is on the x-axis.
    (\textbf{a-b})~Cost of cooperation $c$ is on the y-axis; the cost thresholds $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_thresholds_v_threshold}) are the solid and dashed lines, respectively. 
    (\textbf{c})~Social association $\alpha$ is on the y-axis; the social association thresholds $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting_general_case}) are the solid and dashed lines, respectively.
    Here in figures \textbf{(a)-(c)}, $b=1.3$, $T_A=0.4$, (\textbf{a})~$\alpha = 0$,(\textbf{b})~$\alpha = 0.7$, (\textbf{c})~$c = 0.35$.
    In figure \textbf{(d)} shows stable and unstable polymorphism of cooperation and defection.
    The curves show the change in cooperators frequency, $\hat{p}'-\hat{p}$, as a function of the current frequency of cooperators among juveniles, $\hat{p}$ (\autoref{eq:nextgen_juveniles}).
    A stable polymorphism (orange curve) is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$.
    An unstable polymorphism (blue curve) is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$.
  	}
    \label{fig:equilibria_v1}
\end{figure}
%TODO add panel d?
% maybe show cost vs alpha ?

@@

%%% Figure: polymorphism map
\begin{figure}[p]
  \centering
   % \includegraphics[scale=0.4]{coexistence_without_oblique.eps}
    \includegraphics[scale=0.6]{coexistence_with_oblique.eps}
  \caption{\textbf{Stable and unstable polymorphism of cooperation and defection.}
  The curves show the change in cooperators frequency, $\hat{p}'-\hat{p}$, as a function of the current frequency of cooperators among juveniles, $\hat{p}$ (\autoref{eq:nextgen_juveniles}).
  The dashed black line is $\hat{p}'-\hat{p}=0$.
  The curves and the dashed line intersect at the polymorphic equilibrium $\hat{p}^*$ (red circle).
  %When $\hat{p}' - \hat{p} > 0 $,  $\hat{p}$ increases towards $\hat{p}^*$.
  %When $\hat{p}' - \hat{p} < 0$, $\hat{p}$ decreases towards $\hat{p}^*$.
  A stable polymorphism (orange curve) is given by $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$.
  An unstable polymorphism (blue curve) is given by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $\alpha = 0.09$ and $v=0.6$.
  }
  \label{fig:polymorphism_recursive}
  \end{figure}
